---
title: "Alcohol vs Seat choice"
author: "Luz Vargas"
date: "9/14/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

## methods  
Seat is a categorical variable   
Alcohol is a numerical variable   
For this problem we explain alcohol consumption based on where people sit  
Therefore the helper file we use is the numerical categorical file  

$H_0$: There is no difference in alcohol consumption based on where you sit  

$H_A$: There is a difference in alcohol consumption based on where you sit  


```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
Based on the boxplot, people that sit in the back consume more alcohol than the people who sit in the front and the middle. 


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
Based on the numerical summary evidence shows that people who sit in the back drink an average of 8 drinks a week and on average people who sit in the front and the middle drink about 1-3 drinks a week

## Inferential Tests

## Conclusions


